Manuscript draft

### 2019-06-17 manuscript/manuscript draft.Rmd
updated manuscript draft

$$ ANPP = NPP~stem~ + NPP~branch~ + NPP~canopy~ $$
where NPP~stem~ is the annual woody increment of all stems above a specified diameter at breast height (DBH), NPP~branch~ is annual woody branch turnover, and NPP~canopy~ is annual foliage production, including leaves, twigs, and reproductive structures. ANPP may also include NPP~VOC~, the annual emission of volatile organic compounds, and NPP~herbivory~, the annual consumption of plant matter by herbivores, but these components are often excluded from field observations as they are much harder to quantify. Other components of aboveground productivity that remain largely unquantified include epiphytes, hemiepiphytes, and understory plants [@clark_reviews_2017]. All current ANPP estimates are based on the assumption that the contribution of these components to overall NPP is insignificant.

@@

As discussed above, estimates of NPP, ANPP, and BNPP are generated through summing measurements of their component parts. Since the components included in productivity estimates vary between studies, estimates of productivity were classified within the ForC database according to their components, and then filtered for analysis. Estimates of NPP were selected if they included foliage, branch, stem, coarse root, fine root and optionally understory. Measures of NPP which included additional components were excluded. Estimates of ANPP were selected if they included foliage, stem growth and branch turnover. Any measures of primary productivity where components were unknown were excluded from analysis.

@@

>>>>

$$ ANPP = NPP~stem~ + NPP~branch~ + NPP~canopy~ $$
where NPP~stem~ is the annual woody increment of all stems above a specified diameter at breast height (DBH), NPP~branch~ is annual woody branch turnover, and NPP~canopy~ is annual foliage production, including leaves, twigs, and reproductive structures. ANPP may also include NPP~VOC~, the annual emission of volatile organic compounds, and NPP~herbivory~, the annual consumption of plant matter by herbivores, but these components are often excluded from field observations as they are much harder to quantify. Other components of aboveground productivity that remain largely unquantified include epiphytes, hemiepiphytes, and understory plants [@clark_reviews_2017]. The majority of current ANPP estimates are based on the assumption that the contribution of these components to overall NPP is insignificant.

@@

As discussed above, estimates of NPP, ANPP, and BNPP are generated through summing measurements of their component parts. Since the components included in productivity estimates vary between studies, estimates of productivity were classified within the ForC database according to their components, and then filtered for analysis. Estimates of NPP were selected if they included foliage, branch, stem, coarse root, fine root and optionally understory. Measures of NPP which included additional components, including volatile organic compounds (VOCs), exudates, estimates of NPP lost to herbivory, and the NPP of reproductive structures, were excluded. Estimates of ANPP were selected if they included foliage, stem growth and branch turnover. Any measures of primary productivity where components were unknown were excluded from analysis.

@@

###Discussion

*Challenges in estimating NPP*  
The impact of excluding certain components of NPP on this analysis is unclear, primarily because these components are poorly understood and rarely measured [@clark_net_2001]. Do we want to include a section assessing how much this may or may not impact results?  
1. Hard to measure BNPP because it often isn't sampled deep enough; impact on ratio tests?  
2. Unclear if there are latitudinal patterns e.g. of herbivory/VOCs  
  + Herbivory can be an important component of total NPP so this may be important to account for; likely to be higher in the tropics?
